An Analysis of the Use of Centipawn Loss to Detect Cheating in Chess

### 2022-10-11 Proposal/proposal.tex
fixed hyperlink

Current research \citep{regan2011understanding} has been done by Dr. Kenneth R. Regan, of the Computer Science and Engineering 
Department of the University at Buffalo, employing the use of a model that utilizes the Jenson-Shannon 
Divergence as a basis for detecting player vs. engine games. However, there is much scrutiny over the 
transparency of his methods and their effectiveness on different "intensities" of cheating. There are also 
other open-source options (\href{https://github.com/MGleason1/PGN-Spy}) that can provide an indepth analysis of move-for-move comparisons
in specific games, an area where Dr. Regan's model appears to be weak.

>>>>

Current research \citep{regan2011understanding} has been done by Dr. Kenneth R. Regan, of the Computer Science and Engineering 
Department of the University at Buffalo, employing the use of a model that utilizes the Jenson-Shannon 
Divergence as a basis for detecting player vs. engine games. However, there is much scrutiny over the 
transparency of his methods and their effectiveness on different "intensities" of cheating. There are also 
other \href{https://github.com/MGleason1/PGN-Spy}{open-source options} that can provide an indepth analysis of move-for-move comparisons
in specific games, an area where Dr. Regan's model appears to be weak.
